0_power_analysis

### 2021-11-08 preregistrations/1_pilot/scripts/0_power_analysis.Rmd
final update to data reading pipeline

linear_df <- function(n_subjects, DDM_recovery_correlation, sigma_sd, fixed_effect, n_sim) {
  faux_options(sep=".")
  data_linear <- sim_design(within = list(vars = c("drift_rate_true", "adversity")),
                            n = n_subjects,
                            mu = list(drift_rate_true = 0, adversity = 0),
                            sd = list(drift_rate_true = 1, adversity = 1),
                            r = fixed_effect, plot = FALSE) %>%
    mutate(drift_rate_recov = rnorm_pre(drift_rate_true, mu = mean(drift_rate_true), sd = sd(drift_rate_true), r = DDM_recovery_correlation, empirical = TRUE))

@@

```{r}
tic()
# Grid containing the simulation parameters to loop over
simulation_results_linear <- expand_grid(
  n_subjects = c(400, 450, 500, 550, 600, 800, 1000),
  DDM_recovery_correlation = c(.85),
  sigma_sd = c(0.5, 1),
  fixed_effect =fixed_effect,
  n_sim = 1:500
) %>%
  # simulate data
  mutate(linear_data = future_pmap(., linear_df, .options = furrr_options(seed = TRUE)),
  ) %>%
  # Fit Mixed model to data
  mutate(linear_model = future_map(linear_data, function(x) {

@@

```{r}
power_linear <- simulation_results_linear %>%
  unnest_wider(linear_model) %>%
  group_by(n_subjects, DDM_recovery_correlation) %>%
  # Calculate power
  summarise(
    mixed_true_main_power         = (sum(p_mixed_main_true < .05) / n()) * 100,
    mixed_recov_main_power        = (sum(p_mixed_main_recov < .05) / n()) * 100,
  ) %>%
  ungroup() %>%
  pivot_longer(ends_with("power"), names_to = "effect", values_to = "power")
```

@@

```{r}
power_linear %>%
  mutate(
    effect = case_when(
      effect == "mixed_true_main_power" ~ "True Main Effect",
      effect == "mixed_recov_main_power" ~ "Recovered Main Effect",
    )
  ) %>%
  ggplot(aes(factor(n_subjects), power, color=factor(DDM_recovery_correlation), group = factor(DDM_recovery_correlation))) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = c(80, 90)) +
  #geom_text(aes(label = power)) +
  facet_grid(~effect) +
  theme_classic() +
  labs(
    x = "Sample Size",
    y = "Power",
    color = "DDM Recovery Correlation",
    title = "DDM Power Analysis for Linear Models",
    subtitle = str_c("Beta = ", fixed_effect)
  )
```

>>>>

linear_df <- function(n_subjects, DDM_recovery_correlation, fixed_effect, n_sim) {
  faux_options(sep=".")
  data_linear <- sim_design(within = list(vars = c("drift_rate_true", "adversity")),
                            n = n_subjects,
                            mu = list(drift_rate_true = 0, adversity = 0),
                            sd = list(drift_rate_true = 1, adversity = 1),
                            r = fixed_effect, plot = FALSE) %>%
    mutate(drift_rate_recov = rnorm_pre(drift_rate_true, mu = mean(drift_rate_true), sd = sd(drift_rate_true), r = DDM_recovery_correlation, empirical = TRUE))

@@

```{r}
tic()
# Grid containing the simulation parameters to loop over
simulation_results_linear <- expand_grid(
  n_subjects = c(400, 450, 500, 550, 600, 800, 1000),
  DDM_recovery_correlation = c(.85),
  fixed_effect =fixed_effect,
  n_sim = 1:500
) %>%
  # simulate data
  mutate(linear_data = future_pmap(., linear_df, .options = furrr_options(seed = TRUE)),
  ) %>%
  # Fit Mixed model to data
  mutate(linear_model = future_map(linear_data, function(x) {

@@

```{r}
power_linear <- simulation_results_linear %>%
  unnest_wider(linear_model) %>%
  group_by(n_subjects, fixed_effect) %>%
  # Calculate power
  summarise(
    linear_true_main_power         = (sum(p_mixed_main_true < .05) / n()) * 100,
    linear_recov_main_power        = (sum(p_mixed_main_recov < .05) / n()) * 100,
  ) %>%
  ungroup() %>%
  pivot_longer(ends_with("power"), names_to = "effect", values_to = "power")
```

@@

```{r}
power_linear %>%
  mutate(
    effect = case_when(
      effect == "linear_true_main_power" ~ "True Main Effect",
      effect == "linear_recov_main_power" ~ "Recovered Main Effect",
    )
  ) %>%
  ggplot(aes(factor(n_subjects), power, color=factor(fixed_effect), group = factor(fixed_effect))) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = c(80, 90)) +
  #geom_text(aes(label = power)) +
  facet_grid(~effect) +
  theme_classic() +
  labs(
    x = "Sample Size",
    y = "Power",
    color = "DDM Recovery Correlation",
    title = "DDM Power Analysis for Linear Models",
  )
```
